---
title: "Analyzing the running time performance of PyTorch, `torch`, and `mlr3torch`"
description: |
  Compare the running time performance of PyTorch, `torch`, and `mlr3torch`.
author:
  - name: Carson Zhang
    url: https://carsonzhang.com
format:
  html:
    embed-resources: true
---

```{r}
library(here)
library(flextable)
library(readr)
library(magrittr)
library(dplyr)
```

```{r}
source(here("R", "output_dir_name.R"))
```

```{r}
# TODO: figure out why this doesn't work when you run a second time
result_dir_name = result_dir_name()
result_file_name = here(result_dir_name, "benchmark_results.csv")
benchmark_results = read_csv(result_file_name) %>%
  select(library, total_time)
```

```{r}
# flextable(benchmark_results)

knitr::kable(
  x = benchmark_results,
  digits = 2,
  col.names = c("Library", "Running time (seconds)"))
```


## Appendix

"Instead, we will want to count operations a little more carefully. The unit we will use to describe the running time of an algorithm is the number of atomic operations. This is not exactly a unit of time, but at some level, the atomic operations that we will describe can all be performed in a small number of clock cycles on your CPU and so correspond to a real amount of time.
(Please don’t say runtime as a replacement for running time. These are not the same thing!)" - Sheehy page 56, A First Course in Data Structures using Python
